---
title: "Dog Adoption Survey Results"
author: "John Calzaretta, Aditya Mengani, Jesus Fernandez"
date: "12/06/2022"
output:
  pdf_document: default
  word_document: default
---

```{r install packages, message = FALSE}
install.packages("lmtest")
install.packages("sandwich")
install.packages("AER")
install.packages("patchwork")
install.packages("stargazer")
```

```{r load packages, message = FALSE}
library(stargazer)
library(data.table)
library(sandwich)
library(lmtest)
library(AER) 
library(ggplot2) 
library(patchwork)
library(dplyr)
```

```{r load  data}
d <- fread('../data/das_results_cleaned.csv')
```

## EDA
```{r treatment group balance}
d$msg_treat_str <- ifelse(d$msg_treat_ind==1, "Message", "No Message")
d$any_SI_treat <- ifelse(d$shelter_tp==0, "No Shelter Info", "Some Shelter Info")

d$clustered_treatment_inter <- ifelse(
  (d$msg_treat_ind==0)&(d$any_SI_treat=="No Shelter Info"), "No Message, No Shelter Info", ifelse(
    (d$msg_treat_ind==0)&(d$any_SI_treat=="Some Shelter Info"), "No Message, Some Shelter Info", ifelse(
      (d$msg_treat_ind==1)&(d$any_SI_treat=="No Shelter Info"), "Message, No Shelter Info", 
      "Message, Some Shelter Info")))

d$shelter_nk_treat <- ifelse(d$shelter_tp==1, "Traditional Shelter", "No-Kill Shelter")

# Group by message v no message
d %>% 
  group_by(msg_treat_str) %>%
  summarize(count=n(), mean_rating = mean(rating))

# Group by shelter_type
d %>% 
  group_by(any_SI_treat) %>%
  summarize(count=n(), mean_rating = mean(rating))

# Group by sheleter type (excluding none)
d %>% 
  filter(shelter_tp != 0) %>%
  group_by(shelter_nk_treat) %>%
  summarize(count=n(), mean_rating = mean(rating))

```

# Clustered Treatments
- Message or No Message (applies across all participant-dog ratings)
- No shelter info or some shelter info (applies across all participant-dog ratings)

# Non-Clustered Treatments
- For people w/ some shelter info, each dog is randomly either labeled as traditional or no-kill shelter


# Model 1: Clustered Message Treatment Alone
```{r message treatment model, include=TRUE}
model_msg_base <- d[ , lm(rating ~ factor(msg_treat_ind))]
model_msg_covs<- d[ , lm(rating ~ factor(msg_treat_ind) +
                              factor(age_bin) + 
                              factor(gender) + 
                              factor(marital) + 
                              factor(income_bin) + 
                              factor(own_dog) + 
                              factor(dog_or_cat) + 
                              factor(adopt_or_shop) + 
                              factor(dog_size) + 
                              factor(state) +
                              duration
                              )] # no fixed effects

stargazer(
  model_msg_base,
  model_msg_covs,
  type = 'text', 
  se = list(
    vcovCL(model_msg_base), # <----- clustered standard errors
    vcovCL(model_msg_covs)  # <----- clustered standard errors
  ), omit.stat = c('ser', 'F')
)

```

## Model 2: No Shelter Info (SI) vs Some Shelter Info Treatment
```{r shelter info/no-info treatment model, include=TRUE}
d$any_SI_treat <- ifelse(d$shelter_tp==0, 0, 1)
model_SI_base <- d[ , lm(rating ~ factor(any_SI_treat))]
model_SI_covs<- d[ , lm(rating ~ factor(any_SI_treat) +
                              factor(age_bin) + 
                              factor(gender) + 
                              factor(marital) + 
                              factor(income_bin) + 
                              factor(own_dog) + 
                              factor(dog_or_cat) + 
                              factor(adopt_or_shop) + 
                              factor(dog_size) + 
                              factor(state) +
                              duration
                              )] # <----- no fixed effects

stargazer(
  model_SI_base,
  model_SI_covs,
  type = 'text', 
  se = list(
    vcovCL(model_SI_base), # <----- clustered standard errors
    vcovCL(model_SI_covs)  # <----- clustered standard errors
  ), omit.stat = c('ser', 'F')
)

```

## Model 3: Interaction of Clustered Treatments (Message & Any Shelter Info)
```{r shelter info/no-info treatment model, include=TRUE}
# Create interaction groups for the 2 clustered treatments
d$clustered_treatment_inter <- ifelse(
  (d$msg_treat_ind==0)&(d$any_SI_treat==0), 1, ifelse(
    (d$msg_treat_ind==0)&(d$any_SI_treat==1), 2, ifelse(
      (d$msg_treat_ind==1)&(d$any_SI_treat==0), 3, 4)))

# Models
clust_interaction_base <- d[ , lm(rating ~ factor(clustered_treatment_inter))]
clust_interaction_covs <- d[ , lm(rating ~ factor(clustered_treatment_inter) +
                                    factor(age_bin) + 
                                    factor(gender) + 
                                    factor(marital) + 
                                    factor(income_bin) + 
                                    factor(own_dog) + 
                                    factor(dog_or_cat) + 
                                    factor(adopt_or_shop) + 
                                    factor(dog_size) + 
                                    factor(state) +
                                    duration
                                    )] # no fixed effects

stargazer(
  clust_interaction_base,
  clust_interaction_covs,
  type = 'text', 
  se = list(
    vcovCL(clust_interaction_base), # <----- clustered standard errors
    vcovCL(clust_interaction_covs)  # <----- clustered standard errors
  ), omit.stat = c('ser', 'F')
)

```

## Model 4: Traditional Shelter vs. No-Kill Shelter Info
```{r shelter type model, include=TRUE}
# Filter out any participants with no shelter info
d$shelter_nk_treat <- ifelse(d$shelter_tp==1, 0, 1)

# Create average outcome covariate
d_ao <- d %>%
  group_by(ip) %>%
  summarize(outcome_avg = mean(rating))
d2 <- d %>%
  filter(shelter_tp != 0) %>%
  inner_join(d_ao, by="ip")

# Model
trad_nk_base <- d2[ , lm(rating ~ factor(shelter_nk_treat))]
trad_nk_fixed <- d2[ , lm(rating ~ factor(shelter_nk_treat) +
                              factor(age_bin) + 
                              factor(gender) + 
                              factor(marital) + 
                              factor(income_bin) + 
                              factor(own_dog) + 
                              factor(dog_or_cat) + 
                              factor(adopt_or_shop) + 
                              factor(dog_size) + 
                              factor(state) +
                              duration +
                              outcome_avg # <---- added fixed effects
                              )]

stargazer(
  trad_nk_base,
  trad_nk_fixed,
  type = 'text', 
  se = list(
    vcovCL(trad_nk_base), # <----- clustered standard errors
    vcovCL(trad_nk_fixed) # <----- clustered standard errors
  ), omit.stat = c('ser', 'F')
)
```
